### 2019-07-14 thesis.tex
*** empty log message ***

\chapter{Applications to astrophysical plasmas}
\label{appD}
On Earth, the plasma is considered an exotic state of matter, associated to
the glowing gas inside fluorescent and neon lamps, microchip manufacturing,
research laboratories, and the promise of cleaner and technically infinite
energy source when scientists and engineers manage to succeed at obtaining
a controlled, and energetically efficient, thermonuclear fusion \cite{bell}.
Naturally occurring plasmas in our everyday life are rare, restricted to the
occurrence of lightning during storms, flames, and the beautiful auroras that
take place at high latitudes. In the interplanetary and interstellar space,
however, the situation is the opposite. Starting in the outer layers of
Earth's atmosphere, passing through the solar wind in the interplanetary space,
to the stellar interiors and atmospheres, accretion disks, and molecular clouds
it is estimated that something around $99 \sim 99.9\%$ of the observable matter
is in the plasma state \cite{may}. Therefore, the study and comprehension of
the physics of plasma processes is a fundamental branch of astrophysics.

>>>>

\chapter{Applications to solar plasmas}
\label{appD}
On Earth, the plasma is considered an exotic state of matter, associated to
the glowing gas inside fluorescent and neon lamps, microchip manufacturing,
research laboratories, and the promise of cleaner and technically infinite
energy source when scientists and engineers manage to succeed at obtaining
a controlled, and energetically efficient, thermonuclear fusion \cite{bell}.
Naturally occurring plasmas in our everyday life are rare, restricted to the
occurrence of lightning during storms, flames, and the beautiful auroras that
take place at high latitudes. In the interplanetary and interstellar space,
however, the situation is the opposite. Starting in the outer layers of
Earth's atmosphere, passing through the solar wind in the interplanetary space,
to the stellar interiors and atmospheres, accretion disks, and molecular clouds
it is estimated that something around $99 \sim 99.9\%$ of the observable matter
in the universe is in the plasma state \cite{may,}. Therefore, the study and
comprehension of the physics of plasma processes is a fundamental branch of
astrophysics.

Space plasmas are observed in a broad variety of
